### 2014-02-27 paper/concrete.tex
Isomorphism is most important.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{definition}[Weak isomorphism of information-flow control languages]
  A language \con{|(C, .->, erasef l)|} is \textit{weakly isomorphic} to a
  language \abs{|(iC, .->, erasef l)|} if there exist total functions
  |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|
  |finv .. f = idf iC|.  Furthermore, the following coherence conditions
  must hold:
  \begin{itemize}
    \item |f| is functorial (e.g. if $\abs{x\ R\ y}$ then
    $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
    $l$-equivalences and |.->|, and
    \item |finv| is functorial over $l$-equivalence (though not necessarily |.->|).
  \end{itemize}
  We furthermore call the two languages \textit{isomorphic} if both
  |f| and |finv| are functorial over |.->|.
\end{definition}

>>>>

\begin{definition}[Isomorphism of information-flow control languages]
  A language \con{|(C, .->, erasef l)|} is \textit{isomorphic} to a
  language \abs{|(iC, .->, erasef l)|} if there exist total functions |f
  : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC| |finv
  .. f = idf iC|.  Furthermore, |f| and |finv| are functorial (e.g. if
  $\abs{x\ R\ y}$ then $f(\abs{x})\ \con{R}\ f(\abs{y})$) over both
  $l$-equivalences and |.->|.
\end{definition}

\Red{In some cases, this restriction can be weakened, where |finv| does
not have to be functorial over |.->|}
